\documentclass{article}
\usepackage[utf8]{inputenc}

\title{BCI Assignment 3}
\author{}
\date{October 2019}

\begin{document}

\maketitle

\section{2.4.1 EEG}
\begin{enumerate}
   \item Time domain
   \begin{itemize}
     \item What do you see?
     
     \item What is the average magnitude of EEG fluctuations?
     
     \item When comparing near-by electrodes do the signals look similar (e.g. Oz and O1)?
     
     \item What about when comparing distant electrodes (e.g. Fz versus Oz)?
   \end{itemize}
   \item Frequency domain
   \begin{itemize}
     \item What do you see?
     
     \item Does the power decrease with frequency?
     
     \item Are there any electrodes where this is not the case? If so, what is the location, and
at what frequency does the power increase? (Hint: alpha peak?)
     
   \end{itemize}
\end{enumerate}

\begin{tabular}{ |p{3cm}||p{10cm}| }
 \hline
 \textbf{Task} & \textbf{Observation}\\
 \hline
 \multirow Time-domain  & \\
 \hline
 \multirow Frequency-domain & \\
 \hline
\end{tabular}

\section{2.5.1 External artifacts}
\begin{enumerate}
    \item  Bring up the Sig-Proc-Options window and turn off all pre-processing by setting Preprocessing to None, Spatial filter to None, and Spectral Filter to low-cut-off=0 and highcut-off=inf. What happened, what does the data look like?
    
    \item Turn the Pre-processing to Center. What changed? What do you think this Center option
does?

    \item Switch the Sig-Viewer to time-domain and for each of the following artifacts take a
note of its approximate size (in muV), location (frontal, temporal, central, occipital) and
frequency (speed of fluctuations) as either slow (¡5 Hz) or fast (¿15 Hz):
\end{enumerate}

\begin{tabular}{ |p{3cm}||p{10cm}| }
 \hline
 \textbf{Task} & \textbf{Observation}\\
 \hline
 \multirow Bad channel (i.e.
tapping/removing
an electrode) & \\
 \hline
 \multirow Electrode drift & \\
 \hline
 \multirow Line-noise & \\
 \hline
 \multirow Muscle movement
(i.e., jaw-clenching) & \\
 \hline
 \multirow Eye movement (i.e.,
blinking) & \\
 \hline
 \multirow Eye movement (i.e.,
moving up/down or
left/right) & \\
 \hline
 \multirow Movement (i.e., head
movement) & \\
 \hline
\end{tabular}

\section{2.6.1 Internal artifacts}
\begin{enumerate}
    \item What does detrend do?
    \item Why high-cut-off of 47?
    \item Which changes are associated with the change
in the mental state?
\end{enumerate}

\begin{tabular}{ |p{3cm}||p{10cm}| }
 \hline
 \textbf{Task} & \textbf{Observation}\\
 \hline
 \multirow Eyes open versus closed  & \\
 \hline
\end{tabular}

\section{2.7.1 Referencing}
\begin{tabular}{ |p{3cm}||p{10cm}| }
 \hline
 \textbf{Task} & \textbf{Observation}\\
 \hline
 \multirow None  & \\
 \hline
 \multirow CAR  & \\
 \hline
 \multirow SLAP & \\
 \hline
\end{tabular}







\end{document}
